R Notebook

### 2017-03-10 manuscript/draft.Rmd

* None of the models actually work all that well, compared to baseline.
* Temporal richness variability doesn't track the predictors we use; sites have "inertia"
  * Cite 3 papers Ethan found on consistancy of alpha even when composition changes dramatically
  * Good for absolute accuracy, little room for improvement over baseline
  * Maybe richness is too coarse
    * abundance
    * species-level
* More important to use a reasonable error model than to get the best predictors \& basis expansions
* Ensembles help/don't help (depending on results)
* Point estimate error versus coverage
* In many ways, this is the best-case scenario for SDMs:
  * large data set, known \& consistent sampling technique over a period of decades
  * "True" absences
  * extended predictor set
  * birds arguably migrate quickly enough to make equlibrium \& especially space-for-time assumptions less ridiculous
  * errors for individual species can cancel out; only asking for aggregate values
* Value of stacking versus predicting the quantitity of interest directly
* Need to start doing this, even if we're bad at it.
  * We've posted predictions for the next N years of BBS data, using several methods, and invite others to do so as well.
* Dig around in the residuals for insights

>>>>

* None of the models actually work all that well, compared to baseline.
* Temporal richness variability doesn't track the predictors we use; sites have "inertia"
  * Cite 3 papers Ethan found on consistancy of alpha even when composition changes dramatically
  * Good for absolute accuracy, little room for improvement over baseline
  * Maybe richness is too coarse
    * abundance
    * species-level
* More important to use a reasonable error model than to get the best predictors \& basis expansions
* Ensembles help/don't help (depending on results)
* Point estimate error versus coverage
* In many ways, this is the best-case scenario for SDMs:
  * large data set, known \& consistent sampling technique over a period of decades
  * "True" absences
  * extended predictor set
  * birds arguably migrate quickly enough to make equlibrium \& especially space-for-time assumptions less ridiculous
  * errors for individual species can cancel out; only asking for aggregate values
* Value of stacking versus predicting the quantitity of interest directly
* Need to start doing this, even if we're bad at it.
  * We've posted predictions for the next N years of BBS data, using several methods, and invite others to do so as well.
* Dig around in the residuals for insights
* SDM's and time series models may not be accounting for the ecology of north american birds. Most of them migrate, so whether they are observed or not at the same time every year is a function of their migratory phenology. The migratory patterns of several species have been correlated with NDVI (Renfrew et al 2013).
